### 2013-09-17 results.tex
added error table for imaging axes
latest and greatest results; placeholder for more

Figure~\ref{fig:mr_anatomy} shows the anatomic zones, etc. in ARFI imaging, blah blah blah\ldots

@@

@@

>>>>

Figure~\ref{fig:mr_anatomy} shows the anatomic zones and some anatomic
orientation labels in the prostate of a representative study subject.  The
zonal anatomy of the prostate was manually segmented (Figure XX) across the
image stack, and 3D models of the zonal anatomy volumes were rendered (Figure
XX).

@@

INSERT MR IMAGE SEGMENTS HERE (P79)

INSERT 3D MODEL OF MR HERE

@@

\input{tab_mr_arfi_path_axes}
